### 2022-03-14 02_paper/02_study/paper_methods.Rmd
meeethod section

# select relevant columns
demo.data <- demo.data %>% select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05)

# rename columns
demo.data <- rename(demo.data, c("Group" = "LI06_05",
                                  "Gender" = "LI02_01_1",
                                  "Age" = "LI03_01",
                                  "Teaching Experience" = "LI04_01"))

@@

# changing character into numeric
demo.data$Gender <- as.numeric(demo.data$Gender)

@@

# create new columns that give proportion of Gender
# percentage = female gender divided by all female Gender
demo.data <- demo.data  %>% 
  group_by(Group) %>% 
  mutate(Gender_percentage = Gender/Gender_Sum) %>% 
  mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percentage" = Gender_percentage,
            "M Age in years" = round(mean(Age), 0),
            "SD Age in years" = round(sd(Age), 0),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 0),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 0),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp.in years" = max(`Teaching Experience`),
           )

@@

The expert teachers (`r sum(demo.data$Gender)`women, `r demo.data$Gender_percentage`%) had a mean age of

The participants (98
women; 80%) had a mean age of 23.96 years (SD = 5.82; range:
18–48), and 13 of them (11%) reported to live together with
their child/children. Whereas 21 participants (17%) lived alone,
the remaining participants (n = 102; 83%) lived in a household
consisting of 2–10 persons, with the majority (n = 93)
living in a household of 2–4 persons. At baseline (July
2020), n = 10 participants (8%) reported flu-like symptoms
with one participant being in COVID-related quarantine.

>>>>

# select relevant columns
demo.data <- demo.data %>% select(LI02_01_1,
                                  LI03_01,
                                  LI04_01,
                                  LI06_05,
                                  LI10_05,
                                  LI11_01,
                                  LI13_01,
                                  LI14
                                  )

# rename columns
demo.data <- rename(demo.data, c("Group" = "LI06_05",
                                 "Gender" = "LI02_01_1",
                                 "Age" = "LI03_01",
                                 "Teaching Experience" = "LI04_01",
                                 "Subject" = "LI10_05",
                                 "Semester" = "LI11_01",
                                 "Internship" = "LI13_01",
                                 "Extracurricular Teaching Experience" = "LI14"
                                 ))

@@

# changing character Gender into numeric
demo.data$Gender <- as.numeric(demo.data$Gender)

# changing character Semester into numeric
demo.data$Semester <- as.numeric(demo.data$Semester)

@@

# changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 2, "1","0")

# creating new column with percentage of Extracurricular Teaching Experience
demo.data <- demo.data %>%
  group_by(Group) %>%
  mutate(`Extracurricular Teaching Experience`=n())

# create new columns that give proportion of Gender
# percentage = female gender divided by all female Gender
# demo.data <- demo.data  %>% 
#   group_by(Group) %>% 
#   mutate(Gender_percentage = Gender/Gender_Sum) %>% 
#   mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender female in percentage" = round(sum(Gender/Gender_Sum) * 100, digits = 1),
            "M Age in years" = round(mean(Age), 1),
            "SD Age in years" = round(sd(Age), 1),
            "Min Age in years" = min(Age),
            "Max Age in years" = max(Age),
            "M Exp. in years" = round(mean(`Teaching Experience`), 1),
            "SD Exp. in years" = round(sd(`Teaching Experience`), 1),
            "Min Exp. in years" = min(`Teaching Experience`),
            "Max Exp. in years" = max(`Teaching Experience`),
            "M Semester" = round(mean(Semester), 1),
            "SD Semester" = round(sd(Semester), 1),
            "Min Semester" = min(Semester),
            "Max Semester" = max(Semester),

           )

@@

The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp. in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp. in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp. in years")`).

The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Exp. in years") %>% mean() %>% round(., digits = 1)` years. On average, the student teachers were in their `r demo.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
